\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
divergence error start

    \begin{multline} \label{eq:gradKernel}
        \partial W_h(q(x)) = \\ x \cdot \frac{1}{h \left \| x \right \|} \cdot \frac{1}{\pi h^3} \left\{\begin{matrix}
        - 3q + \frac{9}{4}q^2 & 0 \leqslant q < 1 \\ 
        \\
        - \frac{3}{4}(2-q)^2 & 1 \leqslant q < 2\\ 
        \\
        0 & q \geqslant 2
      \end{matrix}\right.
    \end{multline}
    % maybe specify x here as well

@@

\subsection{Navier-Stokes}
    Navier-Stokes equations describes incompressible fluids and is therefore suitable for SPH simulations. The equations expressed in Lagrangian coordinates can be found in Equation~\ref{eq:nsDensity} and~\ref{eq:nsVelocity}.

    \begin{equation} \label{eq:nsDensity}
        \frac{D\rho}{Dt} = 0 \Leftrightarrow \bigtriangledown \cdot \textbf{v} = 0 
    \end{equation}

    \begin{equation} \label{eq:nsVelocity}
        \frac{D\textbf{v}}{Dt} = \frac{1}{\rho} \bigtriangledown p + v \bigtriangledown ^2 \textbf{v} + \frac{\textbf{f}}{\rho}
    \end{equation}

    In the equations $\frac{D\rho}{Dt}$ and $\frac{D\textbf{v}}{Dt}$ denotes the derivate of the density $\rho$ and the velocity $\textbf{v}$ respectively. The pressure, kinematic viscosity and body forces are denoted by $p,v$ and $\textbf{f}$ respectively. Due to the incompressibility, the partial derivate of the density with respect to the time is zero which implies the equivalence of the equations in~\ref{eq:nsDensity} where the second part $\bigtriangledown \cdot \textbf{v} = 0$ induce that the field is free from divergence.

\subsection{Divergence solver}
\subsection{Density solver}

% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}

>>>>

    \begin{equation} \label{eq:gradKernel}
        \partial W_h(q(x)) =  x \cdot \frac{1}{h \left \| x \right \|} \cdot \frac{1}{\pi h^3} \left\{\begin{matrix}
        - 3q + \frac{9}{4}q^2 & 0 \leqslant q < 1 \\ 
        \\
        - \frac{3}{4}(2-q)^2 & 1 \leqslant q < 2\\ 
        \\
        0 & q \geqslant 2
      \end{matrix}\right.
    \end{equation}
    % maybe specify x here as well

@@

\subsection{Divergence-Free solver}

\begin{comment}
\begin{lstlisting}[language=C++, mathescape=true, escapeinside={(*}{*)}]
function correctDivergenceError
    for all particles $i$ do
        calculateDensityChange $\frac{Dp}{Dt}_i$
    for all particles $i$ do //Scale $\color{codegreen}a_i$
        $a_i = \frac{a_i}{\Delta t}$
    while (t < $t_{max}$) do //Start simulation loop
        adapt time step $\Delta{t}$ 
        for all particles $i$ do //Predict velocities $\color{codegreen}\mathbf{v}_i^*$
            $\mathbf{v}_i = \mathbf{v}_i + \Delta{t}\mathbf{F}_i^{adv}/m_i$
        correctDensityError($\alpha, \mathbf{v}_i$) //Fulfill $\color{codegreen}\rho^* - \rho_0 = 0$
        for all particles $i$ do //Update positions
            $x_i(t + \Delta{t}) = x_i(t) + \Delta{t}\mathbf{v}_i^*$
        for all particles $i$ do //Update neighbourhoods
            find neighbourhoods $N_i(t + \Delta{t})$
        for all particles $i$ do //Update $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$ 
            compute densities $\rho_i(0)$
            compute factors $\alpha_i(0)$
        correctDivergenceError($\alpha, \mathbf{v}^*$) //Fulfill $\color{codegreen}\frac{D\rho}{Dt} = 0$
\end{lstlisting}
\end{comment}

The divergence-free solver ensures the fluid to be free of density change over time by enforcing $\frac{Dp}{Dt} = 0$, which is equivalent to navier-stokes divergence free condition given in equation %\ref{eq:navier}

\subsection{Density solver}

\subsection{Navier-stokes}
% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}
